


\section{Elimination mechanism}

Unlike the British Parliamentary style tournament where you can set the number of rooms depending on how many outrounds you want, and then the teams are exponentially and deterministically eliminated, the Roman Senatorial Debate does not work like that. 

A chamber might fail to resolve the motion, in which case every senator gets 0 points. A chamber might also resolve the motion unanimously without switching sides, in which case every senator gets 3 points. These irregularities pose difficulties to a straightforward elimination mechanism like that in the British Parliamentary style tournament, as a chamber might return all 8 senators with 3 points, or all senators with 0 points. 











\begin{enumerate}
    \item \textbf{Admission to elimination rounds.} At breaks, teams are admitted into the elimination rounds by virtue of the points they've accumulated. 
    \item \textbf{Tie resolution.} In any case where there is a tie, this is to either be resolved by money, or force. In the case where the option to resolve it by force is enabled, any tied member has the right to resolve it by trial by combat. Women may be allowed to fight, but they are accorded the privilege to find a champion. Men are not accorded the privlege of champerty. Champions must be participating senators. This is in line with the general philosophy of the tournament that debate, politics, and intellectualism makes sense only if it is a game of honour - and honour only emerges if there is an ultimate backstop of violence.
    \item \textbf{Points carryover.} Senators will continue to inherit their points from the preliminary rounds. Senators WILL NOT have their accumulated points reset to 0 in the breakrounds. The point of this is to give intellectual autonomy to the senators to stand their ground. 


    \item \textbf{Number of participants.} The number of senators the tournament admits into the outrounds is the number of rounds times 8 senators. we have: 
        \begin{enumerate}
            \item octos (8 strongest rooms, 4th last round): 64 人 $\rightarrow$
            \item quarters (4 strongest rooms, 3rd last round): 32 人 $\rightarrow$ 
            \item semis (2 strongest rooms, 2nd last round): 16 人 $\rightarrow$ 
            \item grand final (last round): 8 人.
        \end{enumerate}
    
    \item \textbf{Elimination mechanism.} In each of the outrounds, the aggregate half of the rooms with the lowest points are eliminated. So unlike BP where the result of each room individually decides the outcome of the outround, here the aggregate result of all rooms in the outround decides the outcome.
    
    
    \item \textbf{The Market of Speech and Influence.} Since senators carry over their points from the preliminary rounds, those with high scores can speak freely with their immediate fear of elimination heavily discounted. This grants intellectual autonomy to top-performing senators, allowing them to assert their own private views with confidence and demonstrate their full intellectual prowess. This means there is now a privilege to speak, where you can basically air your own views on a topic, and you granted an audience. This, on the whole, means that the tournament becomes a market where the commodity of speech and influence can be acquired by a combination of strategic political manoeuvre and careful money management.
    
    \item \textbf{The Grand Final.} How is the winner of the Grand Final determined? This is tricky and it depends on what matters to you. The recommendation is that the you still run the debate as a normal round, but depending on the tournament's interest, one may arbitrarily define the "winner(s)" to be whoever stuck to his guns and whose side resolved the motion. But if for reasons of ceremony or competition the tournament must produce a "winner", they might resolve to define the winner as the side that the chamber resolved in favour for. 
    
   

\end{enumerate}





